Tutorial on running a Graded Response Model

### 2025-08-21 annotated_codes.Rmd
updated Rmd codes

@@

```{r, include=FALSE}
devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
devtools::install_github("masurp/ggmirt")
```

>>>>

This annotated R Markdown file is attached as supplementary material for the tutorial manuscript, which can be downloaded from our [Github repository](https://github.com/rameliaz/grm-tutorial-paper).

@@

```{r, include=FALSE}
devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
```
